Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-06 submission.tex
changes to verbs paragraph

\paragraph{Verbs}
Verbs are inflected for tense (infinitive, present, preterite or past perfect)
in Norwegian and additionally exhibit mood (imperative or indicative; also
conjunctive, however, it is very uncommon and does not occur in the treebank)
and voice (active or passive). Note that both voice and mood have only a single
value in the treebank; \texttt{pass} (passive) and \texttt{imp} (imperative),
respectively.  Verbs which are not passive are implicitly active, and verbs
which are not imperative are indicative.

Table \ref{verbresults} presents the results from tagging and parsing with
modified verb tags. Imperative clauses are fundamentally different from
indicative clauses, as they lack an overt subject, which is reflected in the
fact that mood is the only feature leading to an increase in LAS, with a
reported LAS of 87.04\% Although voice is a very distinguishing property for
verbs, and passive verbs appear in clauses very different from those with
active verbs, introducing this distinction in the tag set leads to a drop in
LAS of 0.05 percentage points.  Distinguishing between the various tenses
yields an LAS of 86.97\%. Combining the two most promising features, mood and
tense, resulted in an LAS of 87.12\% and UAS of 90.31\%.

In an additional experiment, we mapped the verb tenses (and mood, in the case
of imperative) to finiteness. All verbs have finiteness, hence this distinction
has broad coverage. This mapping is syntactically grounded as finite verbs and
nonfinite verbs appear in completely different syntactic constructions, and
proved to greatly improve the parsing, as we saw the overall largest parser
accuracy scores, with 87.30\% for LAS and 90.43\% for UAS, 0.29 and 0.24
percentage points higher than the baseline, respectively. This coincides with
the observations seen for Swedish in \newcite{Ovr:08}, where finiteness was
found to be a very beneficial linguistic feature for parsing.

>>>>

\paragraph{Verbs}
Verbs are inflected for tense (infinitive, present, preterite or past perfect)
in Norwegian and additionally exhibit mood (imperative or indicative; also
conjunctive, however, it is very uncommon and does not occur in the treebank)
and voice (active or passive). Note that both voice and mood have only a single
value in the treebank; \texttt{pass} (passive) and \texttt{imp} (imperative),
respectively. Verbs which are not passive are implicitly active, and verbs
which are not imperative are in indicative mood.

Table \ref{verbresults} presents the results from tagging and parsing with
modified verb tags. Imperative clauses are fundamentally different from
indicative clauses as they lack an overt subject, which is reflected in the
fact that mood is the only feature leading to an increase in LAS, with a
reported LAS of 87.04\%. Although voice is a very distinguishing property for
verbs, and passive clauses are very different from active clauses, introducing
this distinction in the tag set leads to a drop in LAS of 0.05 percentage
points, while distinguishing between the various tenses yields an LAS of
86.97\%. Combining the two most promising features of mood and tense resulted
in an LAS of 87.12\% and UAS of 90.31\%.

In an additional experiment, we mapped the verb tenses (and mood, in the case
of imperative) to finiteness. All verbs have finiteness, hence this distinction
has broad coverage. This mapping is syntactically grounded as finite verbs and
nonfinite verbs appear in completely different syntactic constructions, and
proved to greatly improve the parsing, as we saw the highest parser accuracy
scores of 87.30\% for LAS and 90.43\% for UAS, 0.29 and 0.24 percentage points
higher than the baseline, respectively. This coincides with the observations
seen for Swedish in \newcite{Ovr:08}, where finiteness was found
to be a very beneficial linguistic feature for parsing.
